\vspace{24pt} Comparison of Different Data Layouts for Columnar In-Memory Databases on the Basis of an Example Application

### 2018-08-30 paper/paper.tex
some stuff at benchmarks

\subsubsection{Frame format}
Wang et al.~\cite{wang} have chosen a frame size of 30 seconds. In our opinion, this interval is relatively large. A presented in section \ref{sec:ds} the median frequency of data points is 15 seconds. Therefore, we adopted the frame size. By changing this value, the frame group size increases as well. This would lead to having 484 columns in the frame format table. Querying data becomes an error-prone task. Thus, we decreased the frame group size to ten minutes.

@@

\section{Benchmark Results}

\subsection{Application specific benchmarks}

\subsubsection{timestamps}
\label{sec:bench_ts}

\subsection{Application independent benchmarks}

>>>>

\subsubsection{Frame format}
Wang et al.~\cite{wang} have chosen a frame size of 30 seconds. In our opinion, this interval is relatively large. As presented in section \ref{sec:ds} the median frequency of data points is 15 seconds. Therefore, we adopted the frame size. By changing this value, the frame group size increases as well. This would lead to having 484 columns in the frame format table. Querying data becomes an error-prone task. Thus, we decreased the frame group size to ten minutes.

@@

\section{Benchmark results}
Our application executes several SQL statements. In order to improve their speed, we had to decide for one data storage layout during application development. Therefore, we created some benchmarks, which we want to present in this section. Moreover, we created benchmarks for use cases, that are not relevant for our software.

\subsection{Application specific benchmarks}
In this section we present the benchmark results of the queries directly related to our application.

\subsubsection{timestamps}
\label{sec:bench_ts}
% Ich würde hierzu gerne noch nen Benchmark erstellen

\subsubsection{Get whole trajectory}

\subsubsection{Calculate distances}

\subsubsection{Get points from timeframe}

\subsection{Application independent benchmarks}
We tried to improve the SQL statement performance on many ways. Sometimes our anticipated improvements did not occur. Nevertheless, we want to present those failed optimizations. We also ran queries not related to our application, because we want to have a broader comparison between the different layouts.
